\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

\newcommand{\resumeSubheadingNoItem}[4]{
	\vspace{-1pt}
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
	\end{tabular*}\vspace{-5pt}
}

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Pardhu Sri Rushi Varma Konduru}} & Email: pardhuvarma.cs [at] gmail [dot] com \\
  \href{https://pardhuvarma.tech}{Portfolio: pardhuvarma.tech} & Mobile: Available upon request \\
  \href{https://scholar.google.com/citations?user=Chrj-G0AAAAJ}{Google Scholar,}
  \href{https://github.com/pardhuvarmax}{Github: github.com/pardhuvarmax} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
	\resumeSubheadingNoItem
		{Malla Reddy University Hyderabad}{Hyderabad, India}
		{Bachelor of Technology - Computer Science \& Engineering (Cybersecurity); CGPA: 7.69}{August 2023 - April 2027}
		%{\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Operating Systems, Data Structures, Analysis Of Algorithms, Artificial Intelligence, Machine Learning, Networking, Databases}}}
	    
\vspace{4pt}
\section{Skills Summary}
\resumeSubHeadingListStart
\resumeSubItem{Languages}{Python, Rust, C++, JavaScript, SQL, Bash}
\resumeSubItem{Cybersecurity}{Network Security, Web Security, Vulnerability Assessment \& Penetration Testing (VAPT), Threat Modeling}
\resumeSubItem{Machine Learning}{PyTorch, TensorFlow, Scikit-learn, NLP, Reinforcement Learning, Trustworthy ML}
\resumeSubItem{Systems \& Embedded}{Embedded Systems (ESP32), Microcontroller Programming, Firmware Basics}
\resumeSubItem{Infrastructure \& DevOps}{Docker, Kubernetes, CI/CD Pipelines, Git, Linux Networking, Containerization, Virtualization}
\resumeSubItem{Cloud \& Platforms}{AWS, GCP, Linux, Arduino, ESP32}
\resumeSubItem{Research}{ML Research, Embedded \& Wireless Security Research}
\resumeSubHeadingListEnd

\vspace{-5pt}
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading{Breachpoint CTF 2026}{Online \& Offline}
{Technical Challenge Author \& Cloud Deployment Operations}{Jan 2026 - Mar 2026}
\resumeItemListStart
\resumeItem{Security Challenge Development}
{Designed challenges across Binary Exploitation, Cryptography, Reverse Engineering, Blockchain, Mobile Security, and Steganography.}
\resumeItem{Low-Level Exploitation}
{Engineered vulnerabilities involving memory corruption, race conditions, and adversarial binaries using C/C++ and Assembly.}
\resumeItem{Reverse Engineering \& Analysis}
{Applied static and dynamic analysis techniques using disassembly, debugging, and binary inspection tools.}
\resumeItem{Cross-Language Systems}
{Developed challenges in Python, C/C++, Rust, Go, Kotlin, Solidity, and x86 Assembly to explore attack surfaces.}
\resumeItem{Infrastructure \& Deployment}
{Deployed and managed containerized CTF infrastructure on GCP using Docker, CI/CD pipelines, and GitHub workflows for scalable and reproducible environments.}
\resumeItem{Operational Reliability}
{Maintained infrastructure stability and access control during live competitive environments.}
\resumeItemListEnd

\vspace{1pt}

\resumeSubheading
{Independent ML Research}{Self-Employed}
{Independent ML Researcher}{Dec 2025 - Present}
\resumeItemListStart
\resumeItem{Research Focus}
{Investigating structural robustness, reversible behavioral learning, and parameter-efficient adaptation in neural systems.}
\resumeItem{LoRA-Based Systems}
{Exploring modular low-rank adaptation (LoRA) for controllable, reversible, and safety-oriented AI architectures.}
\resumeItem{Theoretical \& Experimental Work}
{Developing frameworks for reversible adaptation, lifecycle governance, and stability analysis of learned behaviors.}
\resumeItem{Publications \& Prototypes}
{Publishing preprints and building experimental prototypes to evaluate limitations of weight-based learning and emergent behavior control.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{-5pt}
\section{Projects}
\resumeSubHeadingListStart

\resumeSubItem{RLAE Research — Runtime Low-Rank Adaptive Environments}
{Exploring reversible, modular learning systems with externalized behavioral adaptation for controllable and auditable AI architectures.}

\vspace{2pt}

\resumeSubItem{Project Ouroboros (Ouromini) — Embedded Wireless Security Research}
{Designed a modular ESP32-based system for real-time wireless monitoring, analysis, and controlled security experimentation across Wi-Fi and BLE. Developed as a dual-use research testbed for cyber-physical systems and wireless security.}

\vspace{2pt}

\resumeSubItem{EpsilonShift — Adversarial Fingerprint Obfuscation}
{Built a research prototype injecting deterministic adversarial perturbations into browser fingerprinting APIs (Canvas, WebGL, Audio) using Python and Playwright to evaluate privacy defenses.}

\vspace{2pt}

\resumeSubItem{PhishVault — Containerized Phishing Analysis Platform}
{Developed a scalable platform for analyzing and managing malicious URLs with automated reporting and classification. Built using Node.js, MongoDB, Puppeteer, and Docker.}

\vspace{2pt}

\resumeSubHeadingListEnd

\vspace{-5pt}
\section{Publications}
\resumeSubHeadingListStart

\resumeSubItem{On the Structural Limitations of Weight-Based Neural Adaptation and the Role of Reversible Behavioral Learning}
{Pardhu Sri Rushi Varma Konduru. \textit{arXiv preprint - arXiv:2603.02934 (cs.LG, cs.AI), 2026}. Introduces structural irreversibility in weight-based adaptation and proposes reversible behavioral learning with a Recoverability Factor for deterministic rollback. \href{https://arxiv.org/abs/2603.02934}{arXiv} \;|\; \href{https://arxiv.org/pdf/2603.02934}{PDF}}

\resumeSubHeadingListEnd
\vspace{-5pt}
%-----------Awards-----------------
\section{Honors and Awards}
\begin{description}[font=$\bullet$]
	
	\item {2\textsuperscript{nd} Place — GrowthNinja Hackathon (IIT Hyderabad, Tinkers Lab IITH) \hfill Mar 2025}
	\vspace{-3pt}
	\item {15\textsuperscript{th} Place — CY4TF Cyber Fortress CTF (Team Captain, ZenRage; 15/50 teams, 1200 pts) \hfill Mar 2025}
	
\end{description}

\end{document}
